NYC Spatial Models - Comparison of Spatial Models With and Without Twitter Data

### 2019-12-11 analysis/sdm.Rmd
render Rmd

# Obesity model estimation

@@

@@

```{r obesity, echo=FALSE, message=FALSE, warning=FALSE}
# Time consuming.
obese_ls1_sdm <- lagsarlm(update(parks_formula_1, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")
obese_ls2_sdm <- lagsarlm(update(parks_formula_2, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")
obese_ls4_sdm <- lagsarlm(update(parks_formula_4, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")
obese_ls5_sdm <- lagsarlm(update(parks_formula_5, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")

@@

```{r obese_sdm_age_impacts}
devtools::load_all()
obesity_models %>%
  lapply(impacts_extractor) %>%
  bind_rows(.id = "model") %>%
  transmute(model, var, effect,
            output = paste(round(impact, 5),
                           gtools::stars.pval(`p-val`))) %>%
  spread(model, output)
```

>>>>

---
output: github_document
---

<!-- # Obesity model estimation -->

@@

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(geojsonio)
library(tidyverse)
library(maptools)
library(rgdal)
library(rgeos)
library(spdep)
library(texreg)
library(leaflet)
library(sf)
library(VGAM)
```

@@

```{r obesity, echo=FALSE, message=FALSE, warning=FALSE}
ls_names <- c("Short, no tweets",  "Short, tweets",  
              "Long, no tweets",  "Long, tweets")
# Time consuming.
obese_ls1_sdm <- lagsarlm(update(parks_formula_1, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")
obese_ls2_sdm <- lagsarlm(update(parks_formula_2, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")
obese_ls4_sdm <- lagsarlm(update(parks_formula_4, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")
obese_ls5_sdm <- lagsarlm(update(parks_formula_5, OBESITY ~ .), 
                          data = data,  listw = W, zero.policy = TRUE, type = "mixed")

@@

```{r obese_sdm_age_impacts}
# add2pkg::create_desc()
devtools::load_all()
obesity_models %>%
  lapply(impacts_extractor) %>%
  bind_rows(.id = "model") %>%
  transmute(model, var, effect,
            output = paste(round(impact, 5),
                           gtools::stars.pval(`p-val`))) %>%
  spread(model, output)
```
